\documentclass{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}

%\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME


\newcommand{\lineunder} {
	\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header}[1] {
	{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder
}

\newcommand{\employer}[3] {
	{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\paper}[5] {
	{\textbf{#1}\\ \hspace*{15pt}Authors: #2\\ \hspace*{15pt}#3, #4, #5\\ \vspace*{8pt}}
}

\newcommand{\contact}[4] {
	\vspace*{-8pt}\begin{center}{\LARGE \scshape {#1}}\\#2 \lineunder#3 $\bullet$ #4\end{center}\vspace*{-8pt}
}

\newenvironment{achievements} {
	\begin{list}{$\bullet$}
		{\topsep 0pt \itemsep -2pt}
	}{
		\vspace*{4pt}\end{list}
	}

\newcommand{\schoolwithcourses}[4]{
	\textbf{#1} #2 $\bullet$ #3\\
	#4 $\bullet$  Selected Coursework:\\
	\vspace*{5pt}
}

\newcommand{\school}[4] {
	\textbf{#1} #2 $\bullet$ #3\\
	\hspace*{15pt}#4 \\
	\vspace*{5pt}
}

\newcommand{\area}[1] {\textbf{#1:}}

\newcommand{\subject}[1] {\mbox{#1} $\cdot$}

\newcommand{\lastsubject}[1] {\mbox{#1}}

% END RESUME DEFINITIONS

\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Wayne A. Rowcliffe}
{615 W 4th St. Saint Ansgar, IA 50472}
{(641) 832-8396 $\bullet$ wrowclif@gmail.com}%  $\bullet$ http://ugrad.cs.jhu.edu/$\sim$cmichae}
{github: war1025}

\header{About Me}

I thrive on maintenance and refinement. \newline

Once all the trailblazers have swept through and moved on for the latest
and greatest greenfield project, that's where I hit my stride.
Let's flesh this out, mature it, make it do what people actually want,
fix all those glaring performance issues. \newline

I'm a software gardener, groundskeeper. \newline

I've spent the past decade working with a bare bones team to build software
that keeps our customers happy and keeps us in business. \newline

\header{Skills}

	\begin{achievements}
      \item{System architecture and design.}
      \item{Feature development and refinement.}
      \item{Troubleshooting customer issues.}
      \item{Performance optimization.}
      \item{Integrating third party data.}
      \item{Pragmatic problem solving.}
      \item{Addressing workflow bottlenecks and painpoints.}
   \end{achievements}

\header{Technical}

   \begin{achievements}
		\item{Primary Languages:
			\subject{Python}
         \subject{SQL (PostgreSQL)}
			\subject{C++}
			\subject{Typescript}
			\lastsubject{SASS / CSS}
		}
		\item{UI Frameworks:
         \subject{PyQt}
         \lastsubject{Angular}
		}
      \item{Version Control:
         \lastsubject{Git with Pull Requests}
      }
      \item{Development methods:
         \subject{Kanban}
         \subject{Agile (Sprints / Retrospectives)}
         \lastsubject{Continuous Integration (Jenkins)}
      }
      \item{Deployment:
         \subject{Docker}
         \subject{Kubernetes}
         \lastsubject{AWS}
      }
	\end{achievements}

\header{Work History}

   \employer{Priority 5}{2012--Present}{Software Engineer \(\rightarrow\) Senior Engineer \(\rightarrow\) Lead Architect \(\rightarrow\) Head of Engineering}
		\begin{achievements}
         \item{Situational awareness software for government agencies.}
         \item{Client / Server application for geospatial event planning, triage, and response}
         \item{Critical Infrastructure simulation system}
		\end{achievements}

\header{Interesting Work Projects}

	\begin{achievements}
      \item{JSON/Python based query language transpiled to SQL for system dashboarding and analytics.}
      \item{Redis-based, RBAC-aware REST caching layer.}
      \item{Websocket real-time update REST query subscription protocol and backend.}
      \item{Pattern threat detection tool for inter-related data.}
      \item{Integrating all forms of geospatial data. ArcGIS or anything with location data.}
      \item{Maritime AIS transmitter integration for managing shipping ports.}
      \item{Event security staffing and planning tools}
   \end{achievements}

\header{Education}

	\school{Iowa State University}{Ames, IA, U.S.A.}{Bachelor of Science: Software Engineering, 2011}
	{Cumulative GPA: 3.98/4.00}

\header{Honors and Awards}

	\begin{achievements}
		\item{Graduated Summa Cum Laude / Top 2\% of the Engineering College}
	\end{achievements}

\end{document}
